---
title: "Project Analysis Code"
author: "Z - Tomer meshulam & Shimon Peretz"
output: pdf_document
---

```{r load-packages, message = FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(htmltools)
library('DescTools')
library("ggplot2")
library(reshape)
```

```{r setup, include = FALSE}
opts_chunk$set(echo=FALSE) # hide source code in the document
```
# 1. Data
## Importing and showcasing the data
```{r Data import}
students_adp = read.csv(file = 'data/students_adaptability_level_online_education.csv')
summary(students_adp)
```

```{r echo=FALSE}
glimpse(students_adp)
```
# 2. Preliminary results & Data preprocessing
  - Convert categorical variables to numeric:
  - Union of categories
  - Handling null values
```{r , echo=FALSE}
students_adp$Age = factor(students_adp$Age, 
                              levels=c("1-5","6-10","11-15","16-20","21-25","26-30"),
                              labels=c("baby","kids", "teens", "adults", "adults", "adults"))
students_adp$Age = as.numeric(factor(students_adp$Age, 
                              levels=c("baby","kids","teens","adults"),
                              labels=c(1,2, 3, 4)))
students_adp = filter(students_adp, students_adp$Age != 1)

students_adp$Network.Type = factor(students_adp$Network.Type,
                            levels=c("2G", "3G", "4G"), labels=c("slow","slow","fast"))
students_adp$Network.Type = as.numeric(factor(students_adp$Network.Type,
                            levels=c("slow", "fast"), labels=c(1,2)))

students_adp$Education.Level = factor(students_adp$Education.Level,
                              levels=c("University", "College","School"),
                              labels=c("Academic", "Academic","Elementry"))
students_adp$Education.Level = as.numeric(factor(students_adp$Education.Level,
                              levels=c("Academic","Elementry"),
                              labels=c(1,2)))
students_adp$Gender = as.numeric(factor(students_adp$Gender, levels=c("Boy", 
                      "Girl"), labels=c(1,2)))
students_adp$Institution.Type = as.numeric(factor(students_adp$Institution.Type,
                                levels=c("Government", "Non Government"), labels=c(1,2)))
students_adp$IT.Student = as.numeric(factor(students_adp$IT.Student, 
                          levels=c("Yes", "No"), labels=c(1,0)))
students_adp$Location = as.numeric(factor(students_adp$Location,
                        levels=c("Yes", "No"), labels=c(1,0)))
students_adp$Load.shedding = as.numeric(factor(students_adp$Load.shedding,
                             levels=c("Low", "Med", "High"), labels=c(1,2,3)))
students_adp$Financial.Condition = as.numeric(factor(students_adp$Financial.Condition,
                             levels=c("Poor", "Mid", "Rich"), labels=c(1,2,3)))
students_adp$Internet.Type = as.numeric(factor(students_adp$Internet.Type,
                           levels=c("Wifi", "Mobile Data"), labels=c(1,2)))
students_adp$Self.Lms = as.numeric(factor(students_adp$Self.Lms, 
                        levels=c("Yes", "No"), labels=c(1,0)))
students_adp$Device = as.numeric(factor(students_adp$Device,
                      levels=c("Mobile", "Computer", "Tab"), labels=c(1,2, 3)))
students_adp$Adaptivity.Level = as.numeric(factor(students_adp$Adaptivity.Level,
                                levels=c("Low", "Moderate", "High"),
                                labels=c(1,2, 3)))
students_adp$Class.Duration = as.numeric(factor(students_adp$Class.Duration,
                              levels=c("0", "1-3","3-6"), labels=c(1,2, 3)))
```
```{r}
students_adp_nna = drop_na(students_adp)
summary(students_adp_nna)
```

# 3. Data Analysis
## Correlation between the variables of the data-set to the adaptation level

```{r}
res = cor(students_adp_nna)
res
res_df = melt(res)
```
```{r}

ggplot(res_df, aes(x=X2, y=X1, fill=value)) + geom_tile() + 
  scale_fill_gradient(low = "yellow", high = "red") +
  theme(axis.title = element_blank() ,axis.text.x = element_text(angle = 45, hjust =1))

```

## Further-More, we want to see if those important variables are independent:
## we will do that by executing a Chi-square test of independence on each pair.

Tests Features:  
- Significance level (alpha) to: 0.01  
- Null and Alternative Hypotheses:  
* H0: the variables are independent, there is no relationship between the two categorical variables.   
* H1: the variables are dependent, there is a relationship between the two categorical variables.
  
First test: Institution Type and Financial Condition  
- p-value:
```{r , echo=FALSE}
itype_fcond = chisq.test(table(students_adp$Institution.Type,students_adp$Financial.Condition))
itype_fcond$p.value
```
Conclusion: the p-value of the test is Greater-Then the Significance Level
            there for we will reject the Null hypotheses, 
            Institution Type and Financial Condition are dependent

Second test: Institution Type and Class Duration  
- p-value:
```{r , echo=FALSE}
itype_cduration = chisq.test(table(students_adp$Institution.Type,students_adp$Class.Duration))
itype_cduration$p.value
```
Conclusion: the p-value of the test is Less-Then the Significance Level
            there for we will accept the Null hypotheses, 
            Institution Type and Class Duration are independent
            
Third test: Class Duration and Financial Condition  
- p-value:
```{r , echo=FALSE}
cduration_fcond = chisq.test(table(students_adp$Class.Duration,students_adp$Financial.Condition))
cduration_fcond$p.value
```
Conclusion: the p-value of the test is Less-Then the Significance Level
            there for we will accept the Null hypotheses, 
            Class Duration and Financial Condition are independent
            
Fourth test: Network Type and Financial Condition  
- p-value:
```{r , echo=FALSE}
nType_fCond = chisq.test(table(students_adp$Network.Type,students_adp$Financial.Condition))
nType_fCond$p.value
```
Conclusion: the p-value of the test is Less-Then the Significance Level
            there for we will accept the Null hypotheses, 
            Class Duration and Financial Condition are independent
            
## Hypotheses test for mean diffrences between categories inside relevent variables
```{r}
hour = filter(students_adp_nna, students_adp_nna$Class.Duration == 1)
three_hours = filter(students_adp_nna, students_adp_nna$Class.Duration == 2)
six_hours = filter(students_adp_nna, students_adp_nna$Class.Duration == 3)

t.test(hour, three_hours)
t.test(hour, six_hours)
t.test(three_hours, six_hours)

slow = filter(students_adp_nna, students_adp_nna$Network.Type == 1)
fast = filter(students_adp_nna, students_adp_nna$Network.Type == 2)

t.test(slow, fast)
```
## Relevant graphs for  investigate on a high-level the relationship between those variables
and their Adaptivity Level:
```{r}
students_adp = read.csv(file = 'data/students_adaptability_level_online_education.csv')
ggplot(students_adp, aes(y=Class.Duration, fill=Adaptivity.Level)) +
         geom_bar(position = "fill")  +
          scale_fill_manual(values=c("#F0E68C","#FFA500","#FF6347"))+ 
        labs(x = "Proportion", title = "Adaptation Level by Class Duration")

```
```{r , echo=FALSE}
students_adp = read.csv(file = 'data/students_adaptability_level_online_education.csv')
ggplot(students_adp, aes(y=Institution.Type, fill=Adaptivity.Level)) +
         geom_bar(position = "fill")  +
          scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
        labs(x = "Proportion", title = "Adaptation Level by Institution Type")

```
```{r , echo=FALSE}
ggplot(students_adp, aes(y=Financial.Condition, fill=Adaptivity.Level)) +
         geom_bar(position = "fill")  +
          scale_fill_manual(values=c("#87CEEB", "#9370DB", "#FF69B4")) + 
        labs(x = "Proportion", title = "Adaptation Level by Financial Condition")

``` 
```{r , echo=FALSE}
ggplot(students_adp, aes(y=Class.Duration, fill=Adaptivity.Level)) +
         geom_bar(position = "fill")  +
          scale_fill_manual(values=c("#F0E68C","#FFA500","#FF6347"))+ 
        labs(x = "Proportion", title = "Adaptation Level by Class Duration")

```
# Classification Tree Model for predicting Students adaptivity Level
importing relevant packages
```{r}
#install.packages("rpart.plot")
library(rpart)
library(rpart.plot)
```
Fitting decision tree model
```{r}
set.seed(123)
smp_size <- floor(0.75 * nrow(students_adp_nna))
train_ind <- sample(seq_len(nrow(students_adp_nna)), size = smp_size)
train <- students_adp_nna[train_ind, ]
test_results <- students_adp_nna[-train_ind, ]
test <- data.frame(Network.Type = test_results$Network.Type,Class.Duration = test_results$Class.Duration, Financial.Condition = test_results$Financial.Condition)

fit <- rpart(Adaptivity.Level ~ Network.Type+Class.Duration+Financial.Condition, data = train, method = 'class')
rpart.plot(fit)

pred_result <- rpart.predict(fit, newdata = test,type="vector")
exp_result <- test_results$Adaptivity.Level
```
Evaluating the model
```{r}
cm = as.matrix(table(Actucal = exp_result, Predicted = pred_result))
n = sum(cm) # number of instances
nc = nrow(cm) # number of classes
diag = diag(cm) # number of correctly classified instances per class 
rowsums = apply(cm, 1, sum) # number of instances per class
colsums = apply(cm, 2, sum) # number of predictions per class
p = rowsums / n # distribution of instances over the actual classes
q = colsums / n # distribution of instances over the predicted classes


accuracy = sum(diag) / n
precision = diag / colsums 
recall = diag / rowsums 
f1 = 2 * precision * recall / (precision + recall)

matrices = data.frame(accuracy, precision, recall, f1)
rownames(matrices) <- c("Low", "Moderate", "High")
matrices
```
## Source code

```{r, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}

```
